---
title: "HW6"
author: "Tianqi Wu"
date: "4/23/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 5 

## 5(a)
The value of the loglikelihood under the alternative is -420.5813

## 5(b)
Under null, common MLE is 0.05756349, value of the loglikelihood is -454.782

## 5(c)
LRT statistic is 68.40151

## 5(d)
The dimension under alternative assumption is 2 since we have two free parameters. The dimension under null assumption is 1 since we have one free parameter. The degree of freedom is 1.

## 5(e)
At 0.05 significance level with degree freedom of 1, chi-square statistic is 5.02. Since LRT statistic is 68.40151 > 5.02. We reject the null hypothesis that pi's are all equal.

```{r}
## Under alternative
alpha = -2.79558
beta_alter = 0.32726
xi = c(-3,-1,1,3)
pi_alter = 1/(exp(-alpha-beta_alter*xi)+1)
cat('pi_alter:', pi_alter, '\n')
y1 = c(24,35,21,30)
y0 = c(1355,603,192,224)
l_alter = sum(y1*log(pi_alter)+y0*log(1-pi_alter))
cat('l_alter:', l_alter, '\n')

## Under null
b_null = 0
pi_null = 1/(exp(-alpha-b_null*xi)+1)
cat('pi_null:', pi_null, '\n')
l_null = sum(y1*log(pi_null)+y0*log(1-pi_null))
cat('l_null:', l_null, '\n')

## LRT
LRT = 2*(l_alter-l_null)
cat('LRT:', LRT, '\n')
```